Untitled

### 2023-09-23 code/analysis_Redo.Rmd
just playing with some tables

```{r}
library(readxl)
library(did2s)
library(tidyverse)
library(directlabels)
```

@@

dfc %>% 
  filter(Year == 2010) %>% 
  mutate(Treat = ifelse(Att > 0, "Treated", "Control")) %>% 
  select(Treat, Total, Pct.NHA:Pct.COM) %>% 
  filter(complete.cases(.)) %>% 
  tbl_summary(by = Treat, 
                statistic = list(all_continuous() ~ "{mean} ({sd})")) %>% 
  add_p()

>>>>

```{r}
library(readxl)
library(did2s)
library(tidyverse)
library(directlabels)
library(gtsummary)
```

@@

dfc %>% 
  filter(Year == 2010) %>% 
  mutate(Treat = ifelse(Att > 0, "Treated", "Control")) %>% 
  select(Treat, Total, Pct.NHA:Pct.COM) %>% 
  #filter(!complete.cases(.)) %>% 
  tbl_summary(by = Treat, 
                statistic = list(all_continuous() ~ "{mean} ({sd})")) %>% 
  add_p()
